\documentclass[../../../main.tex]{subfiles}
\begin{document}
\subsection{Appendix: Differential Equation Study Guide}
\subsubsection{First Order Equations.} General Form of ODE
\begin{align*}
  \dfrac{dy}{dx}=f(x,y)
\end{align*}

Initial Value Problem
\begin{equation*}
  y'=f(x,y),\ y(x_0) = y_0
\end{equation*}

\subsubsection{Linear Equations.} General Form:
\begin{align*}
  y'+p(x)y=f(x)
\end{align*}
Integrating Factor
\begin{align*}
  \mu(x)   & = e^{\int p(x)dx}                                  \\
  \implies & \dfrac{d}{dx}\left( \mu(x) y \right) = \mu(x) f(x) \\
\end{align*}
General Solution
\begin{equation*}
  y=\frac{1}{\mu(x)}\left( \int \mu(x) f(x) dx + C\right)
\end{equation*}

\subsubsection{Homogeneous Equations.} General form
\begin{align*}
  y'=f(y/x)
\end{align*}
Substitution
\begin{equation*}
  y=zx  \implies y'=z + xz'
\end{equation*}
The result is always separable in $z$:
\begin{equation*}
  \dfrac{dz}{f(z)-z} = \dfrac{dx}{x}
\end{equation*}

\subsubsection{Bernoulli Equations.} General Form
\begin{align*}
  y'+p(x)y=q(x)y^n
\end{align*}
Substitution
\begin{align*}
  z = y^{1-n}
\end{align*}
The result is always linear in $z$:
\begin{equation*}
  z' +(1-n)p(x) z = (1-n)q(x)
\end{equation*}

\subsubsection{Exact Equations.} General Form
\begin{align*}
  M(x,y)dx + N(x,y)dy = 0
\end{align*}
Text for Exactness
\begin{equation*}
  \dfrac{\partial M}{\partial y}=\dfrac{\partial N}{\partial x}
\end{equation*}
Solution
\begin{equation*}
  \phi=C
\end{equation*}
where
\begin{equation*}
  M=\dfrac{\partial \phi}{\partial x}\quad\text{ and }\quad N=\dfrac{\partial \phi}{\partial y}
\end{equation*}

\subsubsection{Method for Solving Exact Equations. }

\begin{enumerate}
  \item Let $\phi=\int M(x,y)dx + h(y)$
  \item Set $\dfrac{\partial \phi}{\partial y} = N(x,y)$
  \item Simplify and solve for $h(y)$
  \item  Substitute the result for $h(y)$ in the expression for $\phi$ from step 1 and then set $\phi=0$. This is the solution.
\end{enumerate}

Alternatively:
\begin{enumerate}
  \item Let $\phi=\int N(x,y)dy + g(x)$
  \item Set $\dfrac{\partial \phi}{\partial x} = M(x,y)$
  \item Simplify and solve for $g(x)$.
  \item Substitute the result for $g(x)$ in the expression for $\phi$ from step 1 and then set $\phi=0$. This is the solution.
\end{enumerate}

\subsubsection{Integrating Factors.} Case 1. If $P(x,y)$ depends only on $x$, where
\begin{equation*}
  P(x,y)=\dfrac{M_y-N_x}{N} \implies \mu(y) = e^{\int P(x)dx}
\end{equation*}
then
\begin{equation*}
  \mu(x) M(x,y) dx + \mu(x) N(x,y) dy = 0
\end{equation*}
is exact.

Case 2. If $Q(x,y)$ depends only on $y$, where
\begin{equation*}
  Q(x,y)=\dfrac{N_x-M_y}{M} \implies \mu(y) = e^{\int Q(y)dy}
\end{equation*}
Then
\begin{equation*}
  \mu(y) M(x,y) dx + \mu(y)N(x,y) dy =0
\end{equation*}
is exact.

\subsubsection{Second Order Linear Equations} General Form of the Equation
\begin{equation}
  a(t)y''+b(t)y'+c(t)y=g(t) \label{eq:general}
\end{equation}
Homogeneous
\begin{equation}
  a(t)y''+b(t)y'+c(t)y=0\label{eq:homog}
\end{equation}
Standard Form
\begin{equation}
  y''+p(t)y'+q(t)y=f(t) \label{eq:ODE}
\end{equation}

\subsubsection{General Solution.} The general solution of \eqref{eq:general} or \eqref{eq:ODE} is
\begin{equation}
  y = C_1 y_1(t) + C_2 y_2 (t) + y_p(t)
\end{equation}
where $y_1(t)$ and $y_2(t)$ are linearly independent solutions of \eqref{eq:homog}.

\subsubsection{Linear Independence and The Wronskian.} Two functions $f(x)$ and $g(x)$ are linearly dependent if there exist numbers $a$ and $b$, not both zero, such that $af(x)+bg(x)=0$ for all $x$. If $y_1$ and $y_2$ are two solutions of \eqref{eq:homog}, then Wronskian
\begin{equation*}
  W(t) = y_1(t) y_2'(t) - y_1'(t) y_2(t)
\end{equation*}
and Abel's Formula
\begin{equation*}
  W(t) = Ce^{-\int{p(t)dt}}
\end{equation*}
and the following are all equivalent:
\begin{enumerate}
  \item $\{y_1,y_2\}$ are linearly independent.
  \item $\{y_1,y_2\}$ are a fundamental set of solutions.
  \item $W(y_1, y_2)(t_0)\neq 0$ at some point $t_0$.
  \item $W(y_1,y_2)(t) \neq 0$ for all $t$.
\end{enumerate}


\subsubsection{Initial Value Problem.} The initial value problem includes two initial conditions at the same point in time, one condition on $y(t)$ and one condition on $y'(t)$.
\begin{equation*}
  \left\{
  \begin{array}{l}
    y''+p(t)y'+q(t)y=0 \\ y(t_0)=y_0 \\ y'(t_0)=y_1
  \end{array}
  \right.
\end{equation*}
The initial conditions are applied to the entire solution $y=y_h+y_p$.

\subsubsection{Linear Equation With Constant Coefficients.} The general form of the homogeneous equation is
\begin{equation}
  ay'' + by' + cy=0 \label{eq:linearhomog}
\end{equation}
Non-homogeneous
\begin{equation}
  ay''+by'+cy = g(t)\label{eq:linearnonhomog}
\end{equation}
Characteristic Equation
\begin{equation*}
  ar^2 + br + c=0
\end{equation*}
Quadratic Roots
\begin{equation}
  r=\frac{-b\pm\sqrt{b^2-4ac}}{2a}
\end{equation}
The solution of \eqref{eq:linearhomog} of Real Roots $(r_1 \neq r_2)$
\begin{equation}
  y_h = C_1 e^{r_1 t} + C_2 e^{r_2t} \label{eq:LH1}
\end{equation}
Repeated $(r_1 = r_2)$
\begin{equation}
  y_h = (C_1 + C_2 t)e^{r_1t}\label{eq:LH2}
\end{equation}
Complex $(r=\alpha\pm i\beta)$
\begin{equation}
  y_H=e^{\alpha t}(C_1 \cos \beta t + C_2 \sin \beta t) \label{eq:LH3}
\end{equation}
The solution of \eqref{eq:linearnonhomog} is $y=y_p+y_h$ where $y_h$ is given by \eqref{eq:LH1} through \eqref{eq:LH3} and $y_p$ is found by undetermined coefficients or reduction of order.

\subsubsection{Heuristics for Undetermined Coefficients.} Also called Trial and Error.
\begin{table}[h]
  \centering
  \caption*{Table: Heuristics method.}
  \begin{tabular}{cc }
    \toprule
    If $f(t)=$               & then guess that a particular solution $y_p=$.           \\
    \midrule
    $P_n(t)$                 & $t^s (A_0 + A_1 t + \cdots + A_n t^n)$                  \\
    $P_n(t)e^{at}$           & $t^s (A_0 + A_1 t + \cdots + A_n t^n)e^{at}$            \\
    $P_n(t)e^{at}\sin bt$    & $t^s e^{at} [(A_0 + A_1 t + \cdots + A_n t^n)\cos bt$   \\
    or $P_n(t)e^{at}\cos bt$ & \ \ \ \ \ $ + (A_0 + A_1 t + \cdots + A_n t^n)\sin bt]$ \\
    \bottomrule
  \end{tabular}
\end{table}


\subsubsection{Method of Reduction of Order.} When solving \eqref{eq:homog}, given $y_1$, then $y_2$ can be found by solving
\begin{equation*}
  y_1 y_2' - y_1'y_2 = Ce^{-\int p(t) dt}
\end{equation*}
The solution is given by
\begin{equation}
  y_2 = y_1\int \dfrac{e^{-\int p(x) dx} dx}{y_1(x)^2}\label{eq:ROE}
\end{equation}

\subsubsection{Method of Variation of Parameters.} If $y_1(t)$ and $y_2(t)$ are a fundamental set of solutions to \eqref{eq:homog} then a particular solution to \eqref{eq:ODE} is
\begin{equation}
  y_P (t) = -y_1(t) \int \dfrac{y_2(t) f(t)}{W(t)}dt + y_2(t) \int \dfrac{y_1(t) f(t)}{W(t)}dt
\end{equation}

\subsubsection{Cauchy-Euler Equation.} For ODE
\begin{equation}
  ax^2y''+bxy'+cy=0 \label{eq:CEODE}
\end{equation}
with auxiliary Equation
\begin{equation}
  ar(r-1)+br+c=0\label{eq:CEODEAux}
\end{equation}
The solutions of \eqref{eq:CEODE} depend on the roots $r_{1,2}$ of \eqref{eq:CEODEAux}. For Real Roots
\begin{equation*}
  y = C_1x^{r_1} + C_2x^{r_2}
\end{equation*}
Repeated Root
\begin{equation*}
  y = C_1 x^r + C_2 x^r \ln x
\end{equation*}
Complex
\begin{equation}
  y=x^{\alpha}[C_1\cos(\beta \ln x) + C_2 \sin (\beta \ln x)] \label{eq:comprootCEODE}
\end{equation}
In \eqref{eq:comprootCEODE} $r_{1,2}=\alpha\pm i\beta$, where $\alpha$,$\beta\in\Re$

\subsubsection{Series Solutions.}
\begin{equation}
  (x-x_0)^2y''+(x-x_0)p(x)y'+q(x)y=0 \label{eq:SS}
\end{equation}
If $x_0$ is a regular point of \eqref{eq:SS} then
\begin{equation*}
  y_1(t) = (x-x_0)^n\sum_{k=0}^{\infty}a_k(x-x_k)^k
\end{equation*}
At a Regular Singular Point $x_0$, the indicial Equation
\begin{equation}
  r^2+(p(0)-1)r + q(0)=0 \label{eq:indicial}
\end{equation}
First Solution
\begin{equation*}
  y_1=(x-x_0)^{r_1}\sum_{k=0}^{\infty}a_k(x-x_k)^k
\end{equation*}
Where $r_1$ is the larger real root if both roots of \eqref{eq:indicial} are real or either root if the solutions are complex.
\end{document}